\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-06 paper/paper.Rnw
Updates

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.sub <- filter(full, subj_id %in% keep)
full.sub$r <- round(full.sub$correlation, 1)
full.sub$rsgn <- ifelse(full.sub$r >= 0, 1, 0)
full.sub$rabs <- abs(full.sub$r)
full.sub$plot <- ifelse(full.sub$test_param == 0, "S", "L")
full.sub <- select(full.sub, subj_id, correct, r, rsgn, rabs, smoothed, n, plot, log_time, response_0, actual_location, pic_id, choice_reason)#[,c(1,7, 15,16,17,20:26)]
full.sub$attempts <- sapply(strsplit(as.character(full.sub$response_0), ","), length)
full.sub$weights = 1/(full.sub$attempts) #weights are actually number of attempts in the glm
full.sub <- full.sub %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
full.sub$correct <- ifelse(full.sub$response_0 == full.sub$actual_location, 1, 0) #fixing correct for multiple guesses
full.sub$alpha <- log(.05/0.95)
full.sub$subj_id <- as.numeric(full.sub$subj_id)
subsetted <- select(full.sub, rabs, n, alpha, rsgn, smoothed, plot, subj_id, weights, correct, log_time)
subsetted$rabs <- as.numeric(subsetted$rabs)
subsetted$subj_id <- as.numeric(subsetted$subj_id)
subsetted <- mutate(subsetted, plot = ifelse(plot=="S", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)

>>>>

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.subs <- filter(full, subj_id %in% keep)
full.subs$r <- round(full.subs$correlation, 1)
full.subs$rsgn <- ifelse(full.subs$r >= 0, 1, 0)
full.subs$rabs <- abs(full.subs$r)
full.subs$plot <- ifelse(full.subs$test_param == 0, "S", "L")
full.subs <- select(full.subs, subj_id, correct, r, rsgn, rabs, smoothed, n, plot, log_time, response_0, actual_location, pic_id, choice_reason)#[,c(1,7, 15,16,17,20:26)]
full.subs$attempts <- sapply(strsplit(as.character(full.subs$response_0), ","), length)
full.subs$weights = 1/(full.subs$attempts) #weights are actually number of attempts in the glm
full.sub <- full.subs %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
full.sub$correct <- ifelse(full.sub$response_0 == full.sub$actual_location, 1, 0) #fixing correct for multiple guesses
full.sub$alpha <- log(.05/0.95)
full.sub$subj_id <- as.numeric(full.sub$subj_id)
subsetted <- select(full.sub, rabs, n, alpha, rsgn, smoothed, plot, subj_id, weights, correct, log_time)
subsetted$rabs <- as.numeric(subsetted$rabs)
subsetted$subj_id <- as.numeric(subsetted$subj_id)
subsetted <- mutate(subsetted, plot = ifelse(plot=="S", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)
